An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-07-17 arxiv/poly-embed.tex
Changed wording of ell2
acks

%\raf{ACKNOWLEDGEMENTS (commented out for submission)}
 \subsection*{Acknowledgements}
 We thank Peter Bartlett for several discussions early on, which led to our 1-dimensional characterization.  %to a proof of %\raf{1-d reduction} among other insights.
 Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
 We thank Eric Balkanski for the insight that led to the proof of Lemma~\ref{lem:bar-f}.
 JF and RF were funded by NSF grant \#1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

>>>>

%\raf{ACKNOWLEDGEMENTS (commented out for submission)}
\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several import insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

### 2019-07-17 neurips-19/poly-embed.tex
About to create merge conflicts
Changed wording of ell2
acks

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
% \subsection*{Acknowledgements}
% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
% Arpit
% Eric Balkanski for a proof of \raf{Lemma on submodularity}
% NSF grant
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

>>>>

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several import insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}
